Review: The Extent of Adaptive Wild Introgression in Crops

### 2018-07-06 paper.tex
edits to Conclusions

Collectively, introgression detection methods have been applied across a wide range of systems, identifying several instances of adaptive introgression.
For example, based on sequence divergence methods, introgression has been detected in \emph{Mimulus} (\emph{i.e.}, monkeyflower) species and appears to play a role in both adaptation to pollinator preference and speciation \cite{Stankowski2015}.
Likewise, the HAPMIX ancestry deconvolution method was applied by Jeong et al. \cite{jeong2014} to detect introgression in human populations from the Nepalese Sherpa to Tibetans at loci controlling high altitude adaptation.
Finally, the ABBA-BABA statistic has revealed introgression at wing coloration loci conferring M\"{u}llerian mimicry across butterfly species \cite{heliconius2012}.
Below we describe the nascent application of these methods to crop systems as well as implications for the study of domestication and adaptation.

@@

As comprehensive genetic analyses of crops and their wild relatives have become feasible across their geographic ranges, evidence for substantial crop-wild introgression has been discovered in some of the world's most important crops (\textbf{Table 2}).
Below we present a summary of findings from maize, barley, rice, and potato, four systems in which crop-wild gene flow appears to have played an adaptive role.
All four of these crops were domesticated in defined centers and have subsequently expanded to much broader distributions, a migration that brought them into contact with new populations of wild relatives (Figure \ref{fig:map}).
Below we describe for each case study what is known about a crop's domestication history and the prevalence of adaptive introgression during post-domestication  expansion.

@@

Recent innovations in both high-density marker data and methods for characterizing genome-wide patterns of introgression have helped reveal the extent and timing of gene flow in a number of species.
Application of these data and techniques has led to mounting evidence of crop-wild gene flow following initial domestication in several crops.
Substantial post-domestication gene flow with wild relatives can affect inferences made regarding domestication and may be an important mechanism through which crops were able to adapt to novel conditions during global expansions.
An accurate understanding of the extent of gene flow is therefore important to both the basic study of crop evolution and to the identification of adaptive alleles for continued crop improvement.

>>>>

Collectively, introgression detection methods have been applied across a wide range of systems, identifying several instances of adaptive introgression (see applications in \textbf{Table 1}).
For example, based on sequence divergence methods, introgression has been detected in \emph{Mimulus} (\emph{i.e.}, monkeyflower) species and appears to play a role in both adaptation to pollinator preference and speciation \cite{Stankowski2015}.
Likewise, the HAPMIX ancestry deconvolution method was applied by Jeong et al. \cite{jeong2014} to detect introgression in human populations from the Nepalese Sherpa to Tibetans at loci controlling high altitude adaptation.
Finally, the ABBA-BABA statistic has revealed introgression at wing coloration loci conferring M\"{u}llerian mimicry across butterfly species \cite{heliconius2012}.
Below we describe the nascent application of these methods to crop systems as well as implications for the study of domestication and adaptation.

@@

As comprehensive genetic analyses of crops and their wild relatives have become feasible across their geographic ranges, evidence for substantial crop-wild introgression has been discovered in some of the world's most important crops (\textbf{Table 2}).
Below we present a summary of findings from maize, barley, rice, and potato, four systems in which crop-wild gene flow appears to have played an adaptive role.
All four of these crops were domesticated in defined centers and have subsequently expanded to much broader distributions, a migration that brought them into contact with new populations of wild relatives (Figure \ref{fig:map}).
For each case study below we describe what is known about both a crop's domestication history and the prevalence of adaptive introgression during post-domestication  expansion.

@@

Recent innovations in both high-density marker data and methods for characterizing genome-wide patterns of introgression have helped reveal the extent and timing of gene flow in a number of species.
Application of these data and techniques has led to mounting evidence of crop-wild gene flow following initial domestication in several crops.
Substantial post-domestication gene flow with wild relatives can affect inferences made regarding domestication and may be an important mechanism through which crops were able to adapt to novel conditions during global expansions.
An accurate understanding of the extent of gene flow is therefore important to both the basic study of crop evolution and to the identification of adaptive alleles for continued crop improvement.
While multiple studies in crop systems have identified wild introgression, fewer have effectively linked introgressed alleles to adaptation.
More comprehensive functional analyses and field evaluation will be critical for understanding the evolutionary and adaptive significance of introgression in crops.
